### 2018-05-11 manuscript.rmd
updated text, figures, formatting

# Improved phylogenetic resolution within Siphonophora (Cnidaria) with implications for trait evolution

@@

## Abstract

Siphonophores are a diverse group of hydrozoans (Cnidaria) that are found at most depths of the ocean - from the surface, like the familiar Portuguese man of war, to the deep sea. Siphonophores play important roles in ocean ecosystems, and are among the most abundant gelatinous predators. A previous phylogenetic study based on two ribosomal RNA genes provided insight into the internal relationships between major siphonophore groups, however there was little support for many deep relationships within the clade Codonophora. Here, we present a new siphonophore phylogeny based on new transcriptome data from 29 siphonophore species analyzed in combination with 14 publicly available genomic and transcriptomic datasets. We use this new phylogeny to reconstruct several traits that are central to siphonophore biology, including sexual system (monoecy vs. dioecy), gain and loss of zooid types, life history traits, and habitat. The phylogenetic relationships in this study are largely consistent with the previous phylogeny, but we find strong support for new clades within Codonophora that were previously unresolved. These results have important implications for trait evolution within Siphonophora, including favoring the hypothesis that monoecy arose at least twice.

## 1. Introduction

@@

## 2. Material and methods

@@

#### 2.1 Collecting

@@

#### 2.2 Sequencing

@@

#### 2.3 Analysis

New data were analysed in conjunction with 14 publicly available datasets [@zapata2015phylogenomic; @Dunn:2013kw; @lehnert2012developing; @philippe2009phylogenomics; @fidler2014unique; @chapman2010dynamic; @sanders2014differential; @putnam2007sea; @sanders2015interspecific], with a total number of 43 species. Sequence assembly, annotation, homology evaluation, gene tree construction, parsing of genes trees to isolate orthologous sequences, and supermatrix construction were conducted with Agalma (commit 6bd9988, running BioLite commit 784edc6) [@Dunn:2013kw; @Guang202416].  This workflow integrates a variety of existing tools [@grabherr2011full; @altschul1990basic; @doi:10.1093/nar/30.7.1575; @sukumaran2010dendropy; @langmead2012fast; @li2011rsem; @talavera2007improvement; @li2009sequence; @katoh2013mafft] and new methods. Maximum likelihood (ML) analyses of the supermatrix were conducted with RAxML v 8.2.0 [@stamatakis2006raxml] and implemented via Agalma. We also used IQTree to implement other ML analyses using different models of substitution to test the robustness of the results to model selection [@doi:10.1093/molbev/msu300; @doi:10.1093/molbev/msx281]. Bayesian Inference (BI) analyses of the supermatrix were conducted using Phylobayes v. 1.7a-mpi [@lartillot2009phylobayes]. Sequence alignments, sampled and consensus trees, and voucher information are available in the git repository. Tree figures were rendered with ggtree [@Yu:2016fo].

@@

@@

## 3. Results and Discussion

### 3.1 Species phylogeny and hypothesis testing

@@

Within Clade A, *Physophora gilmeri* along with *Lychnagalma utricularia* (Fig. \@ref(siphonophores)I) (both not included in the previous phylogeny) are sister to Agalmatidae, a clade restricted to *Agalma*, *Athorybia*, *Melophysa*, *Halistemma* and *Nanomia* [@Dunn:2005dy; @pugh2006taxonomic]. In the rDNA study, *P. hydrostatica* (the presumed sister species to *P. gilmeri*) was sister to Forskaliidae with low support. The position of *Cordagalma cordiforme* (= *Cordagalma ordinatum*) [@pugh2016synopsis] was previously unresolved, while in this analysis *Cordagalma* sp. is in a clade with *Forskalia asymmetrica*, falling outside of Agalmatidae. Placement of *Cordagalma* outside Agalmatidae is consistent with previous analyses of molecular and morphological data [@pugh2006taxonomic; @Dunn:2005dy].

@@

### 3.2 Evolution of Monoecy

@@

### 3.3 The Evolution of Zooid Types

@@

Nectophores (Fig. \@ref(colony)) are non-reproductive propulsive medusae. In Codonophora, the nectophores are localized to a region known as the nectosome (Fig. \@ref(colony)B), which has its own growth zone, and they are used for coordinated colony-level swimming. Planktonic cystonects like *Bathyphysa sibogae* and *Rhizophysa filiformis* (Fig. \@ref(siphonophores)A) instead move through the water column using repeated contraction and relaxation of the stem, and use a gas-filled float and modified flattened gastrozooids with wings (called ptera) to increase surface area and prevent colony sinking [@biggs1976siphonophore].  Nectophores are also present within the gonodendra (reproductive structures) of cystonects, and are thought to propel the gonodendra when they detach from the colony [@totton1965synopsis;@Totton1960]. It is not clear whether the nectophores found within the siphosome of the cystonects are homologous to the nectophores borne on the nectosome of codonophorans. Similarly, the homology of the special nectophore associated with gonophores of the calycophoran *Stephanophyes superba* is also unclear [@chun1891canarischen]. In this study, we only consider the evolution of the nectosome, and not the presence/absence of nectophores. The present analyses, as well as the analyses of @Dunn:2005dy, are consistent with a single origin of the nectosome (Fig. \@ref(fig:nectosome-origin), \@ref(fig:nectosome-BI)).

@@

Bracts are greatly reduced zooids unique to siphonophores, where they are only present in Codonophora (Fig. \@ref(traitdist)). Bracts are functional for protection of the delicate zooids and to help maintain neutral buoyancy [@jacobs1937beobachtungen]. Some calycophorans are able to actively exclude sulphate ions in their bracts to adjust their buoyancy along the colony [@bidigare1980role]. Bracts were lost in Hippopodiidae, some clausophyids, *Physophora hydrostatica* (Fig. \@ref(siphonophores)K), and in *Gymnopraia lapislazula*. These patterns of loss are not captured in this study, as most of these species are not included in the present phylogeny. In species without bracts, other zooids appear to fulfill the roles of neutral buoyancy and protection. In *Physophora hydrostatica*, enlarged palpons surround all other siphosomal zooids and move in a coordinated manner to inflict a powerful sting [@totton1965synopsis]. While in *Hippopodius hippopus* the nectophores play a role in maintaining neutral buoyancy and possibly also in defense, by bioluminescing and blanching in response to stimuli (Fig. \@ref(siphonophores)C shows the blanching of nectophores)[@bassot1978bioluminescence].

Palpons are typically defined as modified reduced gastrozooids [@mackie1987siphonophore]. In many species palpons are thought to play a role in digestion and circulation of the gastrovascular fluid, while other species may use them for defense (e.g _Physophora_) or sensory functions [@totton1965synopsis]. Palpons are subcategorised based on their location - palpons that are associated with gonodendra are termed gonopalpons (typically with a reduced tentacle); palpons found along the stem of the siphosome are termed palpons (typically have a tentacle, called a palpacle); and palpons found along the stem of the nectosome are termed nectosomal palpons (as in _Apolemia_) [@totton1965synopsis;@siebert2013re]. It is not clear how structure and function differs among different palpon subtypes, and a detailed histological investigation of palpons found at different locations within species is needed. For this reason, here we only assess the presence or absence of palpons as a category, without assessing subtypes of palpons. This presumes that palpons located at different regions in the colony are derived from other palpons rather than each arising de novo by independent modification of gastrozooids, a hypothesis that itself could be challenged upon closer histological examination of palpon diversity.

@@

### 3.4 The Gain and Loss of the Pneumatophore

@@

### 3.5 The Gain and Loss of Tentilla

Gastrozooids (specialized feeding polyps) have a single tentacle attached to the base of the zooid that is used for prey capture (with the exception of *Physalia physalis*, which has separate zooids for feeding and prey capture). As in other cnidarians, stinging capsules, arranged in dense batteries of nematocysts, play a critical role in prey capture. In many siphonophore species these batteries are found in side branches of the tentacle, termed tentilla (Fig. \@ref(colony)A).  Outside of Siphonophora, most hydrozoans bear simple tentacles without side branches. It is still an open question whether the common ancestor of Siphonophora had tentilla. The only siphonophores species regarded as lacking tentilla are *Physalia physalis*, *Apolemia* spp. (Fig. \@ref(siphonophores)H), and *Bathyphysa conifera* (Fig. \@ref(siphonophores)B). Since *B. conifera* is the only member of the *Rhizophysidae* (and of the *Bathyphysa* genus) lacking tentilla, we assume this is a case of secondary loss. When we reconstruct the evolution of this character on the current phylogeny, 70% of simulations support a common ancestor bearing tentilla, with two independent losses leading to *Physalia* and *Apolemia* (Fig. \@ref(fig:tentilla), \@ref(fig:tentilla-BI)). However, this leaves a 30% support for a simple-tentacled common ancestor followed by 2 independent gains of tentilla in the branches leading to *Rhizophysidae* and non-apolemiid codonophorans.

How we define absence of tentilla, especially for *Physalia physalis*, is also important. The tentacles of this species, when uncoiled, show very prominent, evenly spaced, bulging buttons which contain in the ectoderm all functional nematocytes (carrying mature nematocysts) used by the organism for prey capture [@Totton1960;@Hessinger1988]. Siphonophore tentilla are complete diverticular branchings of the tentacle ectoderm, mesoglea, and gastrovascular canal (lined by endoderm).  *Physalia*'s buttons enclose individual fluid-filled chambers connected by narrow channels to the tentacular canal, lined by endoderm [@BARDI2007]. This suggests they are not just ectodermal swellings, but probably reduced tentilla. When we define *Physalia physalis* as tentilla bearing, the results for the character reconstruction lead to a more robust support for a tentilla-bearing common ancestor followed by independent losses of tentilla in the branch leading to Apolemiidae (Fig. \@ref(fig:tentilla2), \@ref(fig:tentilla-ext-BI)), and in *Bathyphysa conifera*. The application of phylogenetic methods to the evolution of tentillum morphology would be a crucial step towards understanding the evolution of these structures, and their relationship with the feeding ecology of siphonophores.

### 3.6 The Evolution of Vertical Habitat Use

Siphonophores are abundant predators in the pelagic realm, ranging from the surface (*Physalia physalis*) to bathypelagic depths (Figs. \@ref(traitdist) and \@ref(fig:median-cont)) [@mapstone2014global; @mackie1987siphonophore]. The depth distribution of siphonophore populations is not always static, as some species are known to be vertical migrators, although this is within a relatively narrow depth range (<100m) [@pugh1984diel]. Some species such as *Nanomia bijuga* exhibit synchronous diel migration patterns [@barham1966deep]. Using the present phylogeny, we reconstructed the median depth changes along the phylogeny under a Brownian Motion model (Fig. \@ref(fig:median-depth-extended)), which had the strongest AICc support (compared to non-phylogenetic distributions, and to Ohrnstein-Uhlenbeck). This model indicates a mesopelagic most recent common ancestor, with several independent transition events to epipelagic and bathypelagic waters. There was only a single transition to benthic lifestyle on the branch of Rhodaliidae, and a single transition to a pleustonic lifestyle on the branch of *Physalia physalis*. There is evidence that habitat depth is conserved within some clades, with the exception of Calycophorae which have diversified across the water column (Figs. \@ref(fig:median-cont), \@ref(fig:median-depth-extended), \@ref(fig:depth-BI), \@ref(fig:depth-BI-extended)). Depth appears to be phylogenetically conserved in Euphysonectae after the split between Clade A (shallow-living species) and Group B (deep-dwelling species); however several shallow-living species that likely belong in Group B were not included in this analysis. The present sampling is also not sufficient to capture significant variation in depth distributions between closely related species. Previous studies have shown that many species that are collected at the same locality are found to occupy discrete, largely non-overlapping depth distributions, including between species that are closely related [@pugh1974vertical]. This suggests that vertical habitat use is more labile than it appears and may be an important mechanism in siphonophore ecology. The observed variation in depth distribution could be attributed to any of the correlated environmental variables (i.e. temperature, chlorophyll, oxygen). Temperature has been hypothesized to impose physiological limits to the dispersal of some clausophyid siphonophores [@grossmann2015diversity]. Since we only have oceanographic data from the Monterey Bay region, our analyses cannot disentangle the effects of these different variables on the vertical distributions.

@@

## 4. Conclusions

@@

## Acknowledgements

@@

## Supplementary Information
\setcounter{figure}{0}
\setcounter{table}{0}
\makeatletter
\renewcommand{\thefigure}{S\@arabic\c@figure}
\renewcommand{\thetable}{S\@arabic\c@table}
\makeatother

####Agalma analysis

![\label{gene-occupancy}60% gene occupancy matrix for 41 species across 1,423 genes. Genes and species are sorted by sampling, the best sampled shown in the upper left.](supplementary_info/Supplementary_Figure1.png)

@@

####SOWH analysis

@@

#####Stochastic Character maps

@@

@@

### Software versions

@@

## References

>>>>

# Improved phylogenetic resolution within Siphonophora (Cnidaria) with implications for trait evolution {-}

@@

## Abstract {-}

Siphonophores are a diverse group of hydrozoans (Cnidaria) that are found at most depths of the ocean - from the surface, like the familiar Portuguese man of war, to the deep sea. They play important roles in ocean ecosystems, and are among the most abundant gelatinous predators. A previous phylogenetic study based on two ribosomal RNA genes provided insight into the internal relationships between major siphonophore groups, however there was little support for many deep relationships within the clade Codonophora. Here, we present a new siphonophore phylogeny based on new transcriptome data from 29 siphonophore species analyzed in combination with 14 publicly available genomic and transcriptomic datasets. We use this new phylogeny to reconstruct several traits that are central to siphonophore biology, including sexual system (monoecy vs. dioecy), gain and loss of zooid types, life history traits, and habitat. The phylogenetic relationships in this study are largely consistent with the previous phylogeny, but we find strong support for new clades within Codonophora that were previously unresolved. These results have important implications for trait evolution within Siphonophora, including favoring the hypothesis that monoecy arose at least twice.

## 1. Introduction {-}

@@

## 2. Material and methods {-}

@@

### 2.1 Collecting{-}

@@

### 2.2 Sequencing{-}

@@

### 2.3 Analysis{-}

New data were analysed in conjunction with 14 publicly available datasets [@zapata2015phylogenomic; @Dunn:2013kw; @lehnert2012developing; @philippe2009phylogenomics; @fidler2014unique; @chapman2010dynamic; @sanders2014differential; @putnam2007sea; @sanders2015interspecific], with a total number of 43 species. Sequence assembly, annotation, homology evaluation, gene tree construction, parsing of genes trees to isolate orthologous sequences, and supermatrix construction were conducted with Agalma (commit 6bd9988, running BioLite commit 784edc6) [@Dunn:2013kw; @Guang202416].  This workflow integrates a variety of existing tools [@grabherr2011full; @altschul1990basic; @doi:10.1093/nar/30.7.1575; @sukumaran2010dendropy; @langmead2012fast; @li2011rsem; @talavera2007improvement; @li2009sequence; @katoh2013mafft] and new methods. Maximum likelihood (ML) analyses of the supermatrix were conducted with RAxML v 8.2.0 [@stamatakis2006raxml] and implemented via Agalma. Bayesian Inference (BI) analyses of the supermatrix were conducted using Phylobayes v. 1.7a-mpi [@lartillot2009phylobayes]. Sequence alignments, sampled and consensus trees, and voucher information are available in the git repository. Tree figures were rendered with ggtree [@Yu:2016fo].

@@

To test the robustness of the results to model selection, we also used IQTree to implement other ML analyses using different models of substitution [@doi:10.1093/molbev/msu300; @doi:10.1093/molbev/msx281].  We also evaluated effects of method (ML vs. BI), model, and program by running a fixed-state WAG+$\Gamma$ model in Phylobayes and an ML approximation of CAT models in IQTree.

@@

## 3. Results and Discussion{-}

### 3.1 Species phylogeny and hypothesis testing{-}

@@

Within Clade A, *Physophora gilmeri* along with *Lychnagalma utricularia* (Fig. \@ref(siphonophores)I) (both not included in the previous phylogeny) are sister to Agalmatidae, a clade restricted to *Agalma*, *Athorybia*, *Melophysa*, *Halistemma* and *Nanomia* [@Dunn:2005dy; @pugh2006taxonomic]. In the rDNA study, *P. hydrostatica* (the presumed sister species to *P. gilmeri*) was sister to Forskaliidae with low support. The position of *Cordagalma cordiforme* (= *C. ordinatum*) [@pugh2016synopsis] was previously unresolved, while in this analysis *Cordagalma* sp. is in a clade with *Forskalia asymmetrica*, falling outside of Agalmatidae. Placement of *Cordagalma* outside Agalmatidae is consistent with previous analyses of molecular and morphological data [@pugh2006taxonomic; @Dunn:2005dy].

@@

### 3.2 Evolution of Monoecy {-}

@@

### 3.3 The Evolution of Zooid Types {-}

@@

Nectophores (Fig. \@ref(colony)) are non-reproductive propulsive medusae. In Codonophora, the nectophores are localized to a region known as the nectosome (Fig. \@ref(colony)B), which has its own growth zone, and they are used for coordinated colony-level swimming. Planktonic cystonects like *Bathyphysa sibogae* and *Rhizophysa filiformis* (Fig. \@ref(siphonophores)A) instead move through the water column using repeated contraction and relaxation of the stem, and use a gas-filled float and, in the case of *B. sibogae*, modified flattened gastrozooids with wings (called ptera) to increase surface area and prevent colony sinking [@biggs1976siphonophore].  Nectophores are also present within the gonodendra (reproductive structures) of cystonects, and are thought to propel the gonodendra when they detach from the colony [@totton1965synopsis;@Totton1960]. It is not clear whether the nectophores found within the siphosome of the cystonects are homologous to the nectophores borne on the nectosome of codonophorans. Similarly, the homology of the special nectophore associated with gonophores of the calycophoran *Stephanophyes superba* is also unclear [@chun1891canarischen]. In this study, we only consider the evolution of the nectosome, and not the presence/absence of nectophores. The present analyses, as well as the analyses of @Dunn:2005dy, are consistent with a single origin of the nectosome (Fig. \@ref(fig:nectosome-origin), \@ref(fig:nectosome-BI)).

@@

Bracts are greatly reduced zooids unique to siphonophores, where they are only present in Codonophora (Fig. \@ref(traitdist)). Bracts are functional for protection of the delicate zooids and to help maintain neutral buoyancy [@jacobs1937beobachtungen]. Some calycophorans are able to actively exclude sulphate ions in their bracts to adjust their buoyancy along the colony [@bidigare1980role]. Bracts were lost in Hippopodiidae, some clausophyids, *Physophora hydrostatica* (Fig. \@ref(siphonophores)K), and in *Gymnopraia lapislazula*. These patterns of loss are not captured in this study, as most of these species are not included in the present phylogeny. In species without bracts, other zooids appear to fulfill the roles of neutral buoyancy and protection. In *P. hydrostatica*, enlarged palpons surround all other siphosomal zooids and move in a coordinated manner to inflict a powerful sting [@totton1965synopsis]. While in *Hippopodius hippopus* the nectophores play a role in maintaining neutral buoyancy and possibly also in defense, by bioluminescing and blanching in response to stimuli (Fig. \@ref(siphonophores)C shows the blanching of nectophores)[@bassot1978bioluminescence].

Palpons are typically defined as modified reduced gastrozooids [@mackie1987siphonophore]. In many species palpons are thought to play a role in digestion and circulation of the gastrovascular fluid, while other species may use them for defense (e.g *Physophora*) or sensory functions [@totton1965synopsis]. Palpons are subcategorised based on their location - palpons that are associated with gonodendra are termed gonopalpons (typically with a reduced tentacle, called a palpacle); palpons found along the stem of the siphosome are termed palpons (typically have a tentacle); and palpons found along the stem of the nectosome are termed nectosomal palpons (as in *Apolemia*) [@totton1965synopsis;@siebert2013re]. It is not clear how structure and function differs among different palpon subtypes, and a detailed histological investigation of palpons found at different locations within species is needed. For this reason, here we only assess the presence or absence of palpons as a category, without assessing subtypes of palpons. This presumes that palpons located at different regions in the colony are derived from other palpons rather than each arising *de novo* by independent modification of gastrozooids, a hypothesis that itself could be challenged upon closer histological examination of palpon diversity.

@@

### 3.4 The Gain and Loss of the Pneumatophore {-}

@@

### 3.5 The Gain and Loss of Tentilla {-}

Gastrozooids (specialized feeding polyps) have a single tentacle attached to the base of the zooid that is used for prey capture (with the exception of *Physalia physalis*, which has separate zooids for feeding and prey capture). As in other cnidarians, stinging capsules, arranged in dense batteries of nematocysts, play a critical role in prey capture. In many siphonophore species these batteries are found in side branches of the tentacle, termed tentilla (Fig. \@ref(colony)A).  Outside of Siphonophora, most hydrozoans bear simple tentacles without side branches. It is still an open question whether the common ancestor of Siphonophora had tentilla. The only siphonophores species regarded as lacking tentilla are *P. physalis*, *Apolemia* spp. (Fig. \@ref(siphonophores)H), and *Bathyphysa conifera* (Fig. \@ref(siphonophores)B). Since *B. conifera* is the only member of the *Rhizophysidae* (and of the *Bathyphysa* genus) lacking tentilla, we assume this is a case of secondary loss. When we reconstruct the evolution of this character on the current phylogeny, 70% of simulations support a common ancestor bearing tentilla, with two independent losses leading to *Physalia* and *Apolemia* (Fig. \@ref(fig:tentilla), \@ref(fig:tentilla-BI)). However, this leaves a 30% support for a simple-tentacled common ancestor followed by 2 independent gains of tentilla in the branches leading to *Rhizophysidae* and non-apolemiid codonophorans.

How we define absence of tentilla, especially for *Physalia physalis*, is also important. The tentacles of this species, when uncoiled, show very prominent, evenly spaced, bulging buttons which contain in the ectoderm all functional nematocytes (carrying mature nematocysts) used by the organism for prey capture [@Totton1960;@Hessinger1988]. Siphonophore tentilla are complete diverticular branchings of the tentacle ectoderm, mesoglea, and gastrovascular canal (lined by endoderm).  *Physalia*'s buttons enclose individual fluid-filled chambers connected by narrow channels to the tentacular canal, lined by endoderm [@BARDI2007]. This suggests they are not just ectodermal swellings, but probably reduced tentilla. When we define *P. physalis* as tentilla bearing, the results for the character reconstruction lead to a more robust support for a tentilla-bearing common ancestor followed by independent losses of tentilla in the branch leading to Apolemiidae (Fig. \@ref(fig:tentilla2), \@ref(fig:tentilla-ext-BI)), and in *Bathyphysa conifera*. The application of phylogenetic methods to the evolution of tentillum morphology would be a crucial step towards understanding the evolution of these structures, and their relationship with the feeding ecology of siphonophores.

### 3.6 The Evolution of Vertical Habitat Use {-}

Siphonophores are abundant predators in the pelagic realm, ranging from the surface (*Physalia physalis*) to bathypelagic depths (Figs. \@ref(traitdist) and \@ref(fig:median-cont)) [@mapstone2014global; @mackie1987siphonophore]. The depth distribution of siphonophore populations is not always static, as some species are known to be vertical migrators, although this is within a relatively narrow depth range (<100m) [@pugh1984diel]. Some species such as *Nanomia bijuga* exhibit synchronous diel migration patterns [@barham1966deep]. Using the present phylogeny, we reconstructed the median depth changes along the phylogeny under a Brownian Motion model (Fig. \@ref(fig:median-depth-extended)), which had the strongest AICc support (compared to non-phylogenetic distributions, and to Ohrnstein-Uhlenbeck). This model indicates a mesopelagic most recent common ancestor, with several independent transition events to epipelagic and bathypelagic waters. There was only a single transition to benthic lifestyle on the branch of Rhodaliidae, and a single transition to a pleustonic lifestyle on the branch of *P. physalis*. There is evidence that habitat depth is conserved within some clades, with the exception of Calycophorae which have diversified across the water column (Figs. \@ref(fig:median-cont), \@ref(fig:median-depth-extended), \@ref(fig:depth-BI), \@ref(fig:depth-BI-extended)). Depth appears to be phylogenetically conserved in Euphysonectae after the split between Clade A (shallow-living species) and Group B (deep-dwelling species); however several shallow-living species that likely belong in Group B were not included in this analysis. The present sampling is also not sufficient to capture significant variation in depth distributions between closely related species. Previous studies have shown that many species that are collected at the same locality are found to occupy discrete, largely non-overlapping depth distributions, including between species that are closely related [@pugh1974vertical]. This suggests that vertical habitat use is more labile than it appears and may be an important mechanism in siphonophore ecology. The observed variation in depth distribution could be attributed to any of the correlated environmental variables (i.e. temperature, chlorophyll, oxygen). Temperature has been hypothesized to impose physiological limits to the dispersal of some clausophyid siphonophores [@grossmann2015diversity]. Since we only have oceanographic data from the Monterey Bay region, our analyses cannot disentangle the effects of these different variables on the vertical distributions.

@@

## 4. Conclusions {-}

@@

## Acknowledgements {-}

@@

## Supplementary Information {-}
\setcounter{figure}{0}
\setcounter{table}{0}
\makeatletter
\renewcommand{\thefigure}{S\@arabic\c@figure}
\renewcommand{\thetable}{S\@arabic\c@table}
\makeatother

###Agalma analysis {-}

![\label{gene-occupancy}80% gene occupancy matrix for 41 species across 1,423 genes. Genes and species are sorted by sampling, the best sampled shown in the upper left.](supplementary_info/Supplementary_Figure1.png)

@@

###SOWH analysis {-}

@@

###Stochastic Character maps {-}

@@

###Bayesian models & model fit {-}

@@

### Software versions {-}

@@

## References {-}
